---
title: "The parameters in CASSIA"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Parameters_pCROB}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FLASE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(CASSIA)
dim(parameters_p)
colnames(parameters_p)
```

| Parameter Name   | Meaning   | Reference |
|:----------------:|:---------:|:---------:|
|Q10.N             |           |           |
|Rm.NR            |||
|Q10.S            |||
|Rm.S             |||
|Q10.R            |||
|Rm.R             |||
|sR0              |||
|sRc              |||
|growth.myco      |||
|root.lifetime    |||
|HH0              |||
|sH0              |||
|LH               |||
|LH0              |||
|sHc              |||
|sN0              |||
|LN               |||
|LN0              |||
|sNc              |||
|HN0              |||
|sD0.Trad         |||
|LD               |||
|LD0              |||
|sDc              |||
|sDc.T.count      |||
|tau.Ee           |||
|tau.El           |||
|tau.We           |||
|tau.Wl           |||
|tau.GPP          |||
|Uggla            |||
|sB0              |||
|sBc              |||
|LB               |||
|cell.d.ew        |||
|cell.d.lw        |||
|cell.l.ew        |||
|cell.l.lw        |||
|cell.wall.density.ew  |||
|cell.wall.density.lw  |||
|wall.thickness.ew     |||
|wall.thickness.lw     |||
|cell.volumn.growth.per.day.ew  |||
|cell.volumn.growth.per.day.lw  |||
|density_tree                   |||
|carbon_share                   |||
|D0                             |||
|h0                             |||
|n_age                          |||
|n_lenght                       |||
|h_increment                    |||
|SLA                            |||




